BSTERGMs: Bayesian Separable-Temporal Exponential family Graph Models

### 2020-12-31 doc/paper_format.tex
mod abstract

The Separable Temporal Exponential Random Graph Models (STERGMs)(\cite{RN93}) are useful models to describe changes in dynamic networks' structures evolving over time. 
The Bayesian-inference based approach for the models, however, had not been developed yet. 
In this paper, I propose the Bayesian Separable Temporal Exponential Random Graph Models (BSTERGMs): STERGMs with the Bayesian setting, 
and illustrate a computational algorithm that generates posterior samples from the models dealing with the doubly-intractable constant problem. 
Furthermore, I show an inference method of the models in the Bayesian context.

>>>>

The Separable Temporal Exponential Random Graph Models (STERGMs)(\cite{RN93}) are useful models to describe changes in dynamic networks' structures evolving over time. 
The Bayesian-inference based approach for the models, however, had not been developed yet. 
In this paper, I propose the Bayesian Separable Temporal Exponential Random Graph Models (BSTERGMs): STERGMs with the Bayesian setting, 
and I illustrate a computational algorithm that generates posterior samples from the models dealing with the doubly-intractable constant problem. 
Furthermore, I show an inference method of the models in the Bayesian context.
